The Name of the Title Is Hope

### 2024-03-22 paper/paper.tex
Started writing paper

\author{Mukesh Tiwari}
\affiliation{%
 \institution{Rajiv Gandhi University}
 \streetaddress{Rono-Hills}
 \city{Doimukh}
 \state{Arunachal Pradesh}
 \country{India}}

\author{Berry Schonemark}
\affiliation{%
  \institution{Tsinghua University}
  \streetaddress{30 Shuangqing Rd}
  \city{Haidian Qu}
  \state{Beijing Shi}
  \country{China}}

\author{Bas Spitters}
\affiliation{%
  \institution{The Kumquat Consortium}
  \city{New York}
  \country{USA}}
\email{jpkumquat@consortium.net}

@@

\section{Introduction}
\begin{itemize}
  \item Explain zero-knowledge proofs (completeness, soundness, zero-knowledge)
  \item Explain sigma protocols (completeness, special-soundness, honest-verifier zero-knowledg) 
  and mention about the Schnorr protocol
  \item Our contribution
  \item Explain the Schnorr protocol
  \item Explain Parallel, And, Eq, Or, and NEQ relations (also explain that 
  most of the formalisation has worked on And and Or relations)
\end{itemize}
Zero-knowledge proofs are a class of cryptographic protocols that allow a
prover to convince a verifier that a statement is true without revealing 
any information about the statement itself. 
Zero-knowledge proofs are possible for all problems in the $NP$ complexity class. 
$NP$ includes problems where a proof of membership can be efficiently 
verified in polynomial time. In NP, a witness (denoted as $w$) is a 
polynomial-length piece of evidence that allows quick
verification (in polynomial time) that a given statement $s$ 
belongs to the language. This verification process can be represented 
using a binary relation $R$ between the set of statements (S) and the 
set of witnesses ($W$), where $(s, w) \in R$ if the witness $w$ 
demonstrates that the statement $s$ is in the language.

Sigma protocols were first defined by Ronald Cramer [18],
they are a particularly simple and efficient kind of zero-
knowledge proof and have seen wide deployment; they re-
main a leading kind of proof both in terms of simplicity and
deployment but recent advances in succinct zero-knowledge
proofs [26] offer greater efficiency. The first efficient sigma
protocol was introduced by Schnorr in [38], several years
before the class was defined.

@@

In this paper, we present a 
formal verification of a sigma protocol in the Coq proof assistant. We use 
the Fiat-Crypto library to implement the protocol and prove its security 
properties. Our work is based on the work of \cite{fiat-crypto} and \cite{pok}.

@@

\section{Case Studies}
  We use our formalisation to model the Cryptographic protocols implemented in 
  Helios and Belenois voting systems.

>>>>

\author{Mukesh Tiwari}
\affiliation{%
 \institution{Swansea University}
 \country{United Kingdom}}
 \email{mukesh.tiwari@swansea.ac.uk}

\author{Berry Schoenmakers}
\affiliation{%
  \institution{TU Eindhoven, Eindhoven}
  \country{The Netherlands}}
  \email{l.a.m.schoenmakers@tue.nl}

\author{Bas Spitters}
\affiliation{%
  \institution{Aarhus University}
  \country{Denmark}}
\email{spitters@cs.au.dk}

@@

\section{How to pitch this paper and What is the unique selling point of our work?}
Our Coq formalisation can be used at front-end to generate Web Assembly code and 
Rust code at the back-end. Contrary to the existing work, our formalisation
does not write the same code twice. But sigma protocols are arcane and has 
been formalised couple of times before so why another formalisation?
None of the formalisation has been able to extract the code to executable code 
and one that was able to do so did not reason about probabilities in an intuitive way.
Moreover, that work was just geared towards verifying a transcript rather than
constructing it. Also, recently ZKP community started a movement to 
formalise the Sigma protocols. We also demonstrates the 
applicability of our formalisation by encoding Helios cryptographic protocols
in our formalisation.

\section{Introduction}
Despite the recent growth and popularity of zero-knowledge succinct 
argument of knowledge (ZKSNARK), Sigma protocols remain a
leading cryptographic proof system in privacy-preserving voting systems. 
Sigma protocols are used in Helios, Belenois, and SwissPost voting systems (\textbf{Look for more examples}). 
Moreover, recently ZKP community started a movement to standardise
the Sigma protocols. \textbf{Introduce here that sigma protocols are efficient and simple and all 
other details about sigma protocols.} Sigma protocols allow a prover to convince a verifier that 
they possess some knowledge without revealing anything else about the knowledge itself.  
More formally, for a given relation $R$ and a statement $x$, the prover convinces the verifier
that they posses a witness $w$ such that ($x$, $w$) $\in$ $R$. We would like to stress that
Sigma protocols are a special case of zero-knowledge proofs where the verifier is 
assumed to be honest. Sigma protocols were first defined by Ronald Cramer \cite{cramer1996modular} and the 
first efficient sigma protocol was introduced by Schnorr in \cite{schnorr1991efficient}. 
Eventhough there exists many sigma protocols, the Schnorr protocol is one of the most well-known
sigma protocol and is used extensively in privacy-preserving voting systems, e.g, Helios, SwissPost, etc. 
Therefore, our formalisation is geared towards the Schnorr protocol; moreover, we 
also formalise $n$ PARALLEL composition, $n$ AND composition, $n$ OR composition, 
and $n$ EQ composition of Schnorr protocol. We also formalise Okamoto protocol and 
its $n$ NEQ composition (\textbf{Berry: does it sound okay?}). However, we have not seen 
much use of Okamoto protocol in the privacy-preserving voting systems  (\textbf{Berry: does it sound okay?}), 
at least in the existing voting systems. Ideally, we could have abstracted the sigma protocols and their composition in a generic way,
but we decided to focus on the Schnorr protocol and its composition to ensure a nice APIs in 
Web Assembly and Rust.

There are numerous implementations of Sigma protocols in various languages, 
e.g., Helios is written in Python, Belenois is written in OCaml, and SwissPost is written in Java.
However, there are two main issues with these implementations: (i)  
the same code is written twice 
once for the front-end (JavaScript, TypeScript) and once for the back-end (Python, OCaml, or Java),
especially in privacy-preserving voting systems such as Helios, SwissPost, and 
(ii) none of these implementations offer any formal guarantees about the correctness of the code.
Given the importance of Sigma protocols in privacy-preserving voting systems,
it has been formalised couple of times before  \cite{5552642,butler2019formalisation,10.1145/3319535.3354247}. 
\cite{5552642,butler2019formalisation} are mainly focused on establishing the 
pen-and-paper proofs of Sigma protocols into theorem provers, and not extracting an executable code.
On the other hand, \cite{10.1145/3319535.3354247} exatract an OCaml code from Coq 
formalisation but it is mostly geared towards verifying an Helios election transcript, 
rather than constructing the primitives to conduct an election. Moreover, 
it lacks many primitives and does not reason about probabilities in an intuitive way.

In this paper, we present a formal verification of Sigma protocols in the Coq proof assistant that 
can be used to generate Web Assembly code at the front-end and Rust code at the back-end. 
We use our formalisation to model the cryptographic protocols implemented in Helios voting systems.

\textbf{We need to explain why formal verification is important in the context of voting systems.}

\begin{itemize}
  \item Explain zero-knowledge proofs (completeness, soundness, zero-knowledge)
  \item Explain sigma protocols (completeness, special-soundness, honest-verifier zero-knowledg) 
  and mention about the Schnorr protocol
  \item Our contribution
  \item Explain the Schnorr protocol
  \item Explain Parallel, And, Eq, Or, and NEQ relations (also explain that 
  most of the formalisation has worked on And and Or relations)
\end{itemize}

Zero-knowledge proofs are a class of cryptographic protocols that allow a
prover to convince a verifier that a statement is true without revealing 
any information about the statement itself. 
Zero-knowledge proofs are possible for all problems in the $NP$ complexity class. 
$NP$ includes problems where a proof of membership can be efficiently 
verified in polynomial time. In NP, a witness (denoted as $w$) is a 
polynomial-length piece of evidence that allows quick
verification (in polynomial time) that a given statement $s$ 
belongs to the language. This verification process can be represented 
using a binary relation $R$ between the set of statements (S) and the 
set of witnesses ($W$), where $(s, w) \in R$ if the witness $w$ 
demonstrates that the statement $s$ is in the language.

@@

@@

\section{Case Studies}
  We use our formalisation to model the Cryptographic protocols implemented in 
  Helios voting systems.
